
%% \documentclass[10pt]{article}
%% \usepackage[utf8]{inputenc}
%% \usepackage[english,czech]{babel}
%% \usepackage[T1]{fontenc}
%% \usepackage{charter}
%% \usepackage{times}
%% \usepackage{fullpage}
%% % \usepackage[colorlinks=false]{hyperref}
%% \usepackage[LabelsAligned]{currvita}
%% \usepackage{array}
%% \usepackage{comment}
%% \usepackage[pdftex,a4paper, total={15.3cm,23cm}, top=2.5cm, left=2.8cm, includefoot]{geometry}
%% \usepackage{fancyhdr}                           %custom footer
%% \pagestyle{fancy}
%% % \fancyhf{}
%% \renewcommand{\headrulewidth}{5pt}

%% \usepackage{color}
%%   \usepackage[colorlinks,hyperindex,plainpages=false,pdftex, linkcolor=black,citecolor=black,urlcolor=black,pagecolor=black]{hyperref}
%%   \def\pdfBorderAttrs{/Border [0 0 0] } % bez okrajù kolem odkazù
%%   \pdfcompresslevel=9

%% % Better for lists with 1-2 items and short descriptions
%% \newenvironment{sublist}{%
%% 	\begin{list}{}{%
%% 		\setlength{\itemsep}{0em}\setlength{\parsep}{0em}%
%% 		\setlength{\topsep}{0em}\setlength{\parskip}{0em}%
%% 	}%
%% }%
%% { \end{list} }

%% % Better for lists with more than 2 items and/or long descriptions
%% \newenvironment{subbulletlist}{%
%% 	\begin{list}{\labelitemii}{%
%% 		\setlength{\topsep}{\itemsep}\setlength{\parskip}{\parsep}%
%% 	}%
%% }%
%% { \end{list} }
%% %\newcommand\uv[1]{\quotedblbase \,#1\textquotedblleft}


%% % \pagestyle{empty}
%% % \pagestyle{fancy}
%% \hyphenation{UNIX -- Programming}

%% \renewcommand{\headrulewidth}{5pt} % tloušťka linky

%% % \fancyhf{} % smaže aktuální nastavení záhlaví a zápatí
%% % \fancyhead[LE,RO]{\bf } 
%% % \fancyhead[LO]{\bfseries\rightmark}
%% % \fancyhead[RE]{\bfseries\leftmark}
%% \lhead{Jaroslav Vážný}
%% \rhead{{{Brno PhD talent}}}
%% \renewcommand{\headrulewidth}{0.7pt} % tloušťka linky
%% \renewcommand{\footrulewidth}{0pt}   % patička chybí
%% \addtolength{\headheight}{0.7cm} % prostor pro záhlaví

%% \newlength{\oldcvlabelwidth}
%% \newlength{\oldcvlabelsep}

%% \begin{document}
\begin{cv}
\smallskip
\vspace{-1.2cm}
\begin{center}
 {\large \textsc{Supervisor's Curriculum vitae}\\ 
}\end{center}
 \vspace{-0.1 cm}

% \medskip
\setlength{\oldcvlabelwidth}{\cvlabelwidth}
\setlength{\oldcvlabelsep}{\cvlabelsep}

\setlength{\cvlabelwidth}{1em} 
\noindent\hrulefill
\begin{cvlist}{\large \textsc{Contact}}
\item \begin{tabular}{p{2cm}p{11cm}}  {\bf{Name:}} & RNDr. Petr \v Skoda, CSc.\\
   \end{tabular}
 \item \begin{tabular}{p{2cm}p{11cm}}  
  {\bf{Email:}} & skoda@sunstel.asu.cas.cz\\
   \end{tabular}
  \item \begin{tabular}{p{2cm}p{11cm}}
  {\bf{Office:}} & Astronomical Institute of the Academy of Sciences\\
   \end{tabular}
   \item \begin{tabular}{p{2cm}p{11cm}}
  {\bf{Telephone:}} & +420-323-620361\\
   \end{tabular}
\end{cvlist}

% \noindent\hrulefill
%% \begin{cvlist}{\large \textsc{Personal Information}}
%% \item \begin{tabular}{p{4cm}p{11cm}}  {\bf{Address:}} & Národní 1088, Úpice, 542 32, Czech Republic \end{tabular}
%% \item \begin{tabular}{p{4cm}p{11cm}}  {\bf{Place and date of Birth:}} & Vrchlabí, 4. 8. 1977 \end{tabular}
%   \item \begin{tabular}{p{3cm}p{11cm}}  {\bf{Nationality:}} & Czech \end{tabular}
%\end{cvlist}

% \medskip
% \noindent\hrulefill
%% \begin{cvlist}{\large \textsc{Discipline and a start date of doctoral studies}}
%% \item \begin{tabular}{p{4cm}p{11cm}} {\bf{Discipline:}} & Theoretical Physics and Astrophysics \end{tabular}
%% \item \begin{tabular}{p{4cm}p{11cm}} {\bf{Date of admission:}}  &  28. 7. 2011\end{tabular}
%% \item \begin{tabular}{p{4cm}p{11cm}} {\bf{Date of registration:}} & 28. 7. 2011 (Term: 1, Year: 1)\end{tabular}
%% \end{cvlist}




\begin{cvlist}{\large \textsc{Positions}}

\item Regular member of staff of Stellar Dept. of Astronomical
Institute

\item Since 2000 Member of IAU (participation in  Spectroscopic Virtual 
      Observatory)
 \item Since 2006: Contact person for Virtual observatory in Czech Republic


\end{cvlist}

% % \medskip
\noindent\hrulefill
\begin{cvlist}{\large \textsc{Education and academic qualification}}
\item \begin{tabular}{p{2.8cm}p{11cm}} \vspace{0.2cm} {\bf{1996:}} & \vspace{0.2cm} Received Ph.D. equivalent title CSc. (Candidatus Scientarum) in
astrophysics, Astronomical Institute, PhD. thesis {\it Study of Physical
Processes in Sparse Envelopes of Hot Stars} under supervision of Dr. Hadrava
 \end{tabular}
 \item \begin{tabular}{p{2.8cm}p{11cm}} {\bf{1987--1989:}} & Postgraduate student in Astronomical Institute of the Academy
of Sciences (supervisor Dr. K\v r\'\i{}\v z and Dr. Hadrava)
\end{tabular}
\item \begin{tabular}{p{2.8cm}p{11cm}} {\bf{1987:}} &
Graduated with honors in astrophysics, Thesis {\it A Simple Model
of HII regions}, supervisor Dr. Polechov\'a and Dr. Hadrava

 \end{tabular}

  \item \begin{tabular}{p{2.8cm}p{11cm}} {\bf{1982--1987:}} & Faculty
    of Mathematics and Physics, Charles University (Dept.  of
    Astronomy), Prague

  \end{tabular}
\end{cvlist}
% \setlength{\cvlabelwidth}{0em}
% \setlength{\cvlabelsep}{\labelsep}






% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent\hrulefill
\begin{cvlist}{\large \textsc{Brief employment history}}


\item \begin{tabular}{p{2.8cm}p{11cm}} {\bf{1989--Present:}} &
Regular member of staff of Stellar Dept. of Astronomical
Institute
\end{tabular}

\end{cvlist}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% new page
%\break
\noindent\hrulefill
\begin{cvlist}{\large \textsc{Main research activities}}

%\begin{itemize}
\item Astronomical Instrumentation and Techniques(
Telescope control systems
Optimization of observing and calibration recipes
CCD spectra acquisition and processing)

\item Optical spectroscopy(
Single-order and echelle spectra reduction 
Spectral analysis of (mainly hot) stars
Fourier disentangling and Doppler tomography)

\item Astronomical data archives  and Virtual Observatory
%\end{itemize}

%\begin{itemize}


\item{\bf{\textsc{Selected publications}}}
\item Kor{\v c}\'akov\'a, D., {Mikul\'a\v{s}ek}, Z., {Kawka}, A., {Kub\'at},
J., {Hornoch}, K., {\v{S}arounov\'a}, L., {Ku\v{s}nir\'ak}, P., {Hadrava}, P.,
{Wolf}, M., {\v{S}lechta}, M., {\bf {\v{S}koda}, P}., {Dov\v{c}iak}, M. \&
{Libich}, J. 2005, ``Spectroscopic and Photometric Observations of SN 2004dj'',
{\em Informational Bulletin on Variable Stars\/}, {5605}, 1

\item \v{S}lechta, M., {\bf \v{S}koda, P.} 2005,``An Outburst detected  in the
spectrum of HD~6226'', {\em Astrophys. Space Sci.\/}, 296, 179--182

\item Saad, S.~M., Kub\'at, J., Hadrava, P., Harmanec, P., Koubsk\'y, P., {\bf
\v{S}koda, P.}, \v{S}lechta, M., Kor\v{c}\'akov\'a, D. and Yang, S., 2005,
``Spectrum disentangling and orbital solution  for $\kappa$ Dra, {\em Astrophys.
Space Sci.\/}, 296, 173--177

\item {Chochol}, D., {Katysheva}, N.~A., {Pribulla}, T., {Schmidtobreick}, L.,
{Shugarov}, S.~Y., {\bf{\v S}koda}, P., \v{S}lechta, M., Vittone, A.~A. and
Volkov, I.~M. 2005, ``Photometric and spectroscopic variability of the slow
nova V475 Sct (Nova Scuti 2003)'',  {\em Contributions of Observatory Skalnat\'e
Pleso\/}, 35, 107--129

\item Walker, G. A. H., Kuschnig, R., Matthews, J. M., Reegen, P., Kallinger,
T., Kambe, E., Saio, H. Harmanec, P., Guenther, D. B., Moffat, A. F. J.,
Rucinski, S. M., Sasselov, D., Weiss, W. W., Bohlender, D. A., Bo\v{z}i\'c, H.,
Hashimoto, O., Koubsk\'y, P., Mann, R., Ru\v{z}djak, D., {\bf \v{S}koda, P.},
\v{S}lechta, M., Sudar, D., Wolf, M. \&  Yang, S., 2005, {``
Pulsations of the Oe Star $\zeta$ Ophiuchi from MOST Satellite Photometry 
and Ground-based Spectroscopy''}, {\em Astrophys. J.  Lett.\/}, {623}, {L145--148}

\item {Libich}, J., {Harmanec}, P., {Vondr{\'a}k}, J.,  {Yang}, S., {Hadrava},
P., {Aerts}, C., {de Cat}, P.,  {Koubsk{\'y}}, P., {\bf {\v S}koda, P.}, {{\v
S}lechta}, M.,  {Uytterhoeven}, K. and {Mathias}, P., 2006, ``The new orbital
elements and properties of {$\epsilon$} Persei'', {\em Astronomy and
Astrophys.\/}, 446, 583--589

\item Fr{\'e}mat, Y., {Lampens}, P., {Alecian}, E., {Balona}, L., {Catala}, C.,
{Goupil}, M.-J., {Torres}, G. and {\bf {\v S}koda}, P., 2006,``Spectral
separation of two pulsating non-single stars.'',{\em  Memorie della Societa
Astronomica Italiana\/}, 77, 521--524


\item {Chochol}, D., {Katysheva}, N.~A., {Pribulla}, T., {Schmidtobreick}, L.
, {Shugarov}, S.~Y., {\bf{\v S}koda, P.}, \v{S}lechta, M., Vittone, A.~A. and
Volkov, I.~M. 2006, {``Multicolour Photometry and Spectroscopy of the Slow Nova
V475 Sct (Nova Scuti 2003)''}, Chinese Journal of Astronomy and Astrophysics
Supplement, 6, 137--142

\item Saad, S.~M., Kub\'at, J., Kor\v{c}\'akov\'a, D., Koubsk\'y, P., {\bf
\v{S}koda, P.}, \v{S}lechta, M., Kawka, A., Budovi\v{c}ov\'a, A., Votruba, V.,
\v{S}arounov\'a, L. and Nouh, M.~I., 2006, ``Observation of H{$\alpha$}, iron
and oxygen lines in B, Be and shell stars'', {\em Astron. Astrophys.\/}, 450,
427--430

\item {Linnell}, A.~P., {Harmanec}, P., {Koubsk{\'y}}, P., {Bo{\v z}i{\'c}},
H., {Yang}, S., {Ru{\v z}djak}, D., {Sudar}, D., {Libich}, J., {Eenens}, P.,
{Krpata}, J., {Wolf}, M., {\bf {\v S}koda, P.} and {{\v S}lechta}, M., 2006,
``Properties and nature of Be stars. 24. Better data and model for the Be+F
binary V360 Lacertae'', {\em Astron. Astrophys.\/}, 455, 1037--1052


\item Koubsk\'y, P., Harmanec, P., Yang, S., Netolick\'y, M., {\bf \v{S}koda,
P.}, \v{S}lechta, M. and Kor\v{c}\'akov\'a, D. 2006, ``Properties and nature of
Be stars 25. A new orbital solution and the nature of a peculiar emission-line
binary $\upsilon$~Sqr'', {\em Astron. Astrophys.\/}, 459, 849--857

\item Ak, H., Chadima, P., Harmanec, P., Demircan, O., Yang, S., Koubsk\'y, P.,
{\bf \v{S}koda, P.}, \v{S}lechta, M., Wolf, M., Bozi\'c, H., Ru\v{z}djak, D. and
Sudar, D., 2007, ``New findings supporting the presence of a thick disc and
bipolar jets in the $\beta$~Lyr system'', {\em Astron. Astrophys.\/}, 463,
233--241

\item Harmanec, P., Mayer, P., {Pr{\v s}a}, A., {Bo{\v z}i{\'c}}, H., {Eenens},
P., {Guinan}, E.~F., {McCook}, G., {Koubsk{\'y}}, P., {Ru{\v z}djak}, D.,
{Engle}, S., {Sudar}, D., {\bf {\v S}koda, P.}, {{\v S}lechta}, M., {Wolf}, M.
and {Yang}, S. 2007, ``V379 Cephei: a quadruple system of two binaries'',
{\em Astron. Astrophys.\/}, 463, 1061--1069

\item Kub\'at, J., Kor\v{c}\'akov\'a, D., Kawka, A., Pigulski, A., \v{S}lechta,
M., {\bf \v{S}koda, P.}, 2007, {``The H$\alpha$ stellar and interstellar
emission in the open cluster NGC 6910''}, {\em Astron.  Astrophys.}, 
472, 163--167

\item {\bf \v{S}koda, P.}, 2007, {``The Virtual Observatory and its Benefits 
for Amateur Astronomers''}, {\em Open European Journal on Variable Stars}, 75, 32--36


\item {\bf \v{S}koda, P.}, {Kub\'at}, J. ,{Votruba}, V., {\v{S}lechta}, M.,
	{Podskalsk\'y}, Z. and {Kart\'ak}, M., 2007, {``Nova Vulpeculae 2007''},
  {\em Central Bureau Electronic Telegrams}, 1035, 1

\item {{Mikul{\'a}{\v s}ek}, Z.,  {Krti{\v c}ka}, J., {Henry}, G.~W. 
, {Zverko}, J., {\v{Z}i{\v z}{\v n}ovsk{\'y}}, J., 
        {Bohlender}, D., {Romanyuk}, I.~I., {Jan{\'{\i}}k}, J., 
        {Bo{\v z}i{\'c}}, H., {Kor{\v c}{\'a}kov{\'a}}, D., {Zejda}, M., 
        {Iliev}, I.~K., {\bf {\v S}koda, P.}, {{\v S}lechta}, M.,
        {Gr{\'a}f}, T., {Netolick{\'y}}, M. and {Ceniga}, M.}
2008, {``The extremely rapid rotational braking of the magnetic helium-strong star HD 37776''}, 
{\em Astron. Astrophys.\/}, 485, 585--597


\item 
{\bf {\v S}koda, P.} 2009, {``Identification of important VO spectral services 
benefiting from deployment on the Grid .''},{\em Memorie della Societa 
Astronomica Italiana}, 80, 484--492

 
\item
{Hadrava, P., {\v S}lechta, M., and {\bf {\v S}koda, P.}} 2009, {``Notes on 
disentangling of spectra. II. Intrinsic line-profile variability due to 
Cepheid pulsations''},{\em Astronomy and Astrophysics}, 507, 397--404 


\item {Shore, S.~N., Wahlgren, G.~M., Genovali, K., Bernabei, S., Koubsky, P., 
{\v S}lechta, M., {\bf {\v S}koda, P.}, Skopal, A., and Wolf, M.} 2010, {``The 
spectroscopic evolution of the symbiotic star AG Draconis. I. The O VI 
Raman, Balmer, and helium emission line variations during the outburst of 
2006-2008''},{\em Astron. Astrophys.},510, A70 



\end{cvlist}

\noindent\hrulefill
\begin{cvlist}{\large \textsc{Pedagogical activities}} \addtolength{\itemsep}{-0.5\baselineskip}
\item Reviewer of attendant bachelor thesis
\item Supervisor of attendant Master's thesis
\item Supervisor of attendant PhD thesis
\item Seminars about technology of Virtual Observatory 
 \item \hspace{0.5cm} Institute of Astronomy University of Vienna, March 2008
\item \hspace{0.5cm} Institute of Astronomy, Bulgarian Academy of Sciences, Sofia, December 2009
\item\hspace{0.5cm}  Crimean Astrophysical observatory, Nauchnyi, September 2010
\end{cvlist}

\noindent\hrulefill
\begin{cvlist}{\large \textsc{Awards and Recognitions}}
\item 
\end{cvlist}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent\hrulefill
\begin{cvlist}{\large \textsc{Other relevant information}}
\item{\bf{\textsc{Participation in Grant Projects}}}


\item 1991--1993, GA \v CSAV, 30318: "The Nature and Structure of the
Circumstellar Matter in Binary Stars"

\item 1998--2000, M\v SMT: LB98251: "Public Information System of Astronomical
Electronic Data", {\bf Principal Investigator}


\item 1998--2002, GA~AV\v CR A3003805: "Spectroscopic Studies of Binary and
Multiple Stars"

\item 2002--2004, GA\v CR 205/02/0445: "Physics of Hot Stars and Stellar
Systems with Hot Components"

\item 2002--2004, GA\v CR 102/02/1000: "The Development of Ond\v rejov Echelle
Spectrograph",

\item 2003--2005, GA\v CR 205/03/0778: "Asymmetry of Be-Star Envelopes"

\item 2004--2006, GA\v{C}R 205/04/1267: "Circumstellar Envelopes of Hot
Stars"

\item 2006--present, GA\v{C}R 205/06/0584: "The Precise High Dispersion
Spectroscopy of Hot Stars", {\bf Principal Investigator} 

\item 2006--present, EURO-VO DCA , supported by WP6

\item 2007--present, ESA PECS 98058: "Czech Participation in the Gaia Project"

%\end{itemize}
\vspace{1ex}


\end{cvlist}
\end{cv}
%\end{document}

